When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-03-01 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
added model comparison anova results

The model had an effect size of $f^{2}=$`r round(h2b_level_f2, digits = 2)` for the *n*-back levels and $f^{2}=$`r round(h2b_dprime_f2, digits = 2)` for *d'*, which are considered large and small, respectively [@Cohen1992].
This means that the *n*-back level explained `r paste0(formatC(h2b_level_f2 * 100, format = "f", digits = 2), "%")` and *d'* explained `r paste0(formatC(h2b_dprime_f2 * 100, format = "f", digits = 2), "%")` of variance in SVs relative to the unexplained variance, respectively.
The effect size of the median RT was $f^{2}=$`r format(round(h2b_medianRT_f2, digits = 2), nsmall = 2)`.
The beta coefficients indicated that with every *n*-back level, the SV decreased by `r as.numeric(h2b_result.table[2,"Beta"])`, and for every 1-unit increase in *d'*, the SV increased by `r as.numeric(h2b_result.table[3,"Beta"])`.

@@

INSERT FIGURE 4 HERE
<!--
```{r h3a-plot, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Difference scores in the subjective values of 1- minus 2-back and of 2- minus 3-back.", fig.pos="H"}

  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "h3a-plot.png"))

>>>>

We used an ANOVA to compare the fit of the final model with a linear random intercept model.
The two models were different from each other ($\chi^2(`r compare_h2b$Df[2]`)=compare_h2b$Chisq[2]$, $p<.001$), and with an Akaike Information Criterion of $AIC=`r compare_h2b$AIC[2]`$ and a Bayesian Information Criterion of $BIC=`r compare_h2b$BIC[2]`$ the declining logistic model is superior to the linear model ($AIC=`r compare_h2b$AIC[1]`$, $BIC=`r compare_h2b$BIC[1]`$).
The model had an effect size of $f^{2}=$`r round(h2b_level_f2, digits = 2)` for the *n*-back levels and $f^{2}=$`r round(h2b_dprime_f2, digits = 2)` for *d'*, which are considered large and small, respectively [@Cohen1992].
This means that the *n*-back level explained `r paste0(formatC(h2b_level_f2 * 100, format = "f", digits = 2), "%")` and *d'* explained `r paste0(formatC(h2b_dprime_f2 * 100, format = "f", digits = 2), "%")` of variance in SVs relative to the unexplained variance, respectively.
The effect size of the median RT was $f^{2}=$`r format(round(h2b_medianRT_f2, digits = 2), nsmall = 2)`.
The beta coefficients indicated that with every *n*-back level, the SV decreased by `r as.numeric(h2b_result.table[2,"Beta"])`, and for every 1-unit increase in *d'*, the SV increased by `r as.numeric(h2b_result.table[3,"Beta"])`.

@@

INSERT FIGURE 4 HERE
